\huge Microbial Interaction Database pipeline - Figures draft \#2

### 2018-12-19 figures.tex
Move figure4 to figures2
Update figure4

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure4.pdf}
  \caption{Effect of OTU processsing measures on the OTU table. This is just a placeholder}
  \label{fig:figure4}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure5.pdf}
  \caption{
    \textbf{Networks generated using different network inference methods}.
    The four different networks generated by different network inference methods are very dissimilar (C).
    (A) The overlaps between the edges among the network5 generated is shown. The number of edges that are common to all networks are very low (5).
    (B) The hamming distance between the networks is shown. The similarity between various methods was found to vary with the data-source used.
}
  \label{fig:figure5}
\end{figure}

@@

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figure4.pdf}
  \caption{
    \textbf{Networks generated using different network inference methods}.
    \textbf{(A)} The four different networks generated by different network inference methods are very dissimilar
    \textbf{(B)} The edge overlap upset plot
    \textbf{(C)} The node overlap upset plot.
  }
  \label{fig:figure4}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\linewidth]{figures2.pdf}
  \caption{Effect of OTU processsing measures on the OTU table. This is just a placeholder}
  \label{fig:figures2}
\end{figure}
